---
title: "R Notebook"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(PKPDdatasets) # devtools::install_github('dpastoor/PKPDdatasets') 
library(NonCompart)
```

# One-compartment pharmacokinetic data given single oral dose (N=50)

## Description

A dataset containing dose, plasma concentration and time data, as well as demographic data of Age, Weight, Gender, and Race for each individual

## Format
A data frame with 4300 rows and 9 variables

## Details
- ID. Numerical ID (1–50)
- Time. Time in hours (0–24)
- Amt. Amount of drug given, time dependent, in milligrams
- Conc. Plasma concentration in mg/L 
- Age. Age in years 
- Weight. Weight in kg 
- Gender. Male or Female gender identification 
- Race. Ethnicity 
- Dose. Dose given to each individual in milligrams

```{r}
data_raw <- PKPDdatasets::sd_oral_richpk %>% 
  as_tibble() %>% 
  print()
```

```{r}
data_raw %>% 
  ggplot(aes(Time, Conc, group = ID, color = Weight)) +
  geom_line() +
  geom_point() +
  facet_grid(rows = vars(Gender), cols = vars(Race)) +
  theme_bw() +
  labs(title = 'Oral administration', 
       x='Time (h)',
       y='Concentration (mg/L)')
```

```{r noncompartmental}
tblNCA(as.data.frame(data_raw),
       key = 'ID',
       'Time',
       'Conc')
```





